Something about correlation functions

### 2021-06-24 paper-correlations.tex
More on pore size function

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
% When cleveref fails to do its job
\newcommand{\apref}[1]{Appendix \ref{#1}}

@@

These correlation functions are calculated using two different approaches (when
applicable). The first approach is implemented in the module \code{Directional}
and the second approach is in the module \code{Map}. The former approach (called
the scan approach) calculates correlation functions along specified directions
which can include axial and diagonal directions. The results of computations can
be provided to the user separately for each requested direction or averaged over
multiple directions. The latter approach (called the map approach) calculates a
``correlation map'' which stores the values of a correlation function in all
directions. The scan and map approaches are described in \cref{scansec} and
\cref{mapsec} respectively.

@@

As you can see this function cannot be obtained from one-dimensional slices.

>>>>

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
% When cleveref fails to do its job
\newcommand{\apref}[1]{Appendix \ref{#1}}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

These correlation functions are calculated using two different approaches (when
applicable). The first approach is implemented in the module \code{Directional}
and the second approach is in the module \code{Map}. The former approach (called
the scan approach) calculates correlation functions along specified directions
which can include axial and diagonal directions. The results of computations can
be provided to the user separately for each requested direction or averaged over
multiple directions. The latter approach (called the map approach) calculates a
``correlation map'' which holds the values of a correlation function in all
directions. The scan and map approaches are described in \cref{scansec} and
\cref{mapsec} respectively.

@@

As you can see this function cannot be obtained from one-dimensional slices. We
calculate it using distance transform. For each point $\bm{x}$ distance
transform $\mathcal{D}(\bm{x})$ is defined as
\begin{equation*}
  \mathcal{D}(\bm{x})= \left\{
  \begin{array}{ll}
    0 & \quad \bm{x} \in \text{solid phase} \\
    \argmin\limits_{y \in \text{solid phase}} \rho(\bm{x},\bm{y}) & \quad \text{otherwise}
  \end{array}
\right.
\end{equation*}

Our algorithm for calculating $P(r)$ for a two-phase system is the following:
\begin{algorithmic}[1]
  \Procedure{poresize}{$array, nbins$}
    \State $d \gets dist(array)$ \Comment{$dist$ calculates
      $\mathcal{D}(\bm{x})$ for each element of $array$}
    \State $f(x) \gets x \ne 0$
    \State $positive \gets filter(d, f)$
    \State Bin values in $positive$ to $nbins$ bins to compute a histogram $H$
    \State \textbf{return} $H$
  \EndProcedure
\end{algorithmic}
